From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-08 Pi+/paper/finite.tex
Revise some things in the appendix
Fix immersion normal form example-proof

\begin{definition}[$\Lehmer : \Nat \to \UU$]
  \begin{align*}
    \Lehmer[\zero]   & \defeq \Fin[\suc[\zero]]                     \\
    \Lehmer[\suc[n]] & \defeq \Fin[\suc[\suc[n]]] \times \Lehmer[n]
  \end{align*}
  % \begin{aligned}
  %   \lzero & : \Lehmer[\zero]                                                     \\
  %   \lsuc  & : \forall n, r, (r \leq \suc[n]) \to \Lehmer[n] \to \Lehmer[\suc[n]]
  % \end{aligned}
\end{definition}

@@

\jk{Review:}
To see that Lehmer codes under $\immersion$ are normal with respect to $\longcoxstar$, let us look at the example code $c =
  (4, 3, 2, 1, 0)$. The list $\immersion(c)$ is then going to be $[0, 1, 0, 2, 1, 0, 3, 2, 1, 0, 4, 3, 2, 1, 0]$. It is a
concatenation of five decreasing lists. Where could a reduction happen?

First, it can't happen inside any of the decreasing components: $\longcancel$ requires repeating elements, $\longswap$
acts when a smaller number precedes a larger one, and $\longbraid$ has a non-monotone sequence on the left. This leaves
the case of a reduction happening on a fragment that borders two subsequences. Again, $\longcancel$ requires two equal
consecutive numbers, which have to be the last one in some decreasing sequence, and the first one in the next sequence.
But the first number in a sequence is always larger than every number in the sequence before it -- which also shows why
$\longswap$ cannot happen. The remaining case of $\longbraid$ follows similarly, since it requires the number appearing
after the decreasing sequence to be equal to the first one in the sequence.

>>>>

\begin{definition}[$\Lehmer : \Nat \to \UU$]
  \begin{align*}
    \Lehmer[\zero]   & \defeq \Fin[\suc[\zero]]                     \\
    \Lehmer[\suc[n]] & \defeq \Lehmer[n] \times \Fin[\suc[\suc[n]]]
  \end{align*}
  % \begin{aligned}
  %   \lzero & : \Lehmer[\zero]                                                     \\
  %   \lsuc  & : \forall n, r, (r \leq \suc[n]) \to \Lehmer[n] \to \Lehmer[\suc[n]]
  % \end{aligned}
\end{definition}

@@

\begin{proof}
\jk{Only for part 1 of the proposition!}
For any code $c : \Lehmer[n]$, we have that 
\[
  \immersion(n, c) = (r_0 \downf k_0) \append (r_1 \downf k_1) \append \dots \append (r_{m-1} \downf k_{m-1})
\]
is concatenation of $m \geq 0$ non-empty strictly decreasing lists. Reduction $\longcox$ cannot happen inside any of the strictly
decreasing $(r \downf k)$: $\longcancel$ requires repeating elements, $\longswap$ acts when consecutive numbers differ
by at least 2, and $\longbraid$ acts on a non-monotone sequence. This leaves the case of reduction happening on a
fragment that borders two (or more) subsequences. Again, $\longcancel$ requires two equal consecutive numbers, which
would then have to be the last one in some $(r_i \downf k_i)$ sequence, and the first one in the next $(r_{i+1} \downf k_{i+1})$.
But the first number in a sequence $(r_{i+1} \downf k_{i+1})$ is larger than every number in $(r_{i} \downf k_i)$ -- which also
shows why $\longswap$ cannot happen. The remaining case of $\longbraid$ follows similarly, since its argument is a
decreasing sequence followed immediately by a number equal to the first element of this sequence.
\end{proof}
% \jk{Review:}
% To see that Lehmer codes under $\immersion$ are normal with respect to $\longcoxstar$, let us look at the example code
% $c = (0, 1, 2, 3, 4)$ -- for the full proof, see accompanying Agda code. We have that 
% \[
%   \immersion(c) = (0 \downf 1) \append (0 \downf 2) \append (0 \downf 3) \append (0 \downf 4) = [0, 1, 0, 2, 1, 0, 3, 2, 1, 0]
% \]
% is concatenation of four decreasing lists . Where could a reduction happen?

% First, it can't happen inside any of the strictly decreasing $(n \downf k)$: $\longcancel$ requires repeating elements,
% $\longswap$ acts when consecutive numbers differ by at least 2, and $\longbraid$ acts on a non-monotone
% sequence. This leaves the case of reduction happening on a fragment that borders two (or more) subsequences. Again,
% $\longcancel$ requires two equal consecutive numbers, which would then have to be the last one in some $(0 \downf k)$
% sequence, and the first one in the next $(0 \downf \suc[k])$. But the first number in a sequence $(0 \downf \suc[k])$ is
% larger than every number in $(0 \downf k)$ -- which also shows why $\longswap$ cannot happen. The remaining case of
% $\longbraid$ follows similarly, since its argument is a decreasing sequence followed immediately by a number equal to
% the first element of the list.
